BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-20 tex/2-algorithms.tex
Done.

Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\alph*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
\end{enumerate}
Web feeds usually contain about 20 blog posts~\cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in the web feed.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building \emph{extraction rules} from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.

% input from observations.
Observation~\ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date. We call these fields \emph{targets} as they constitute the data our crawler aims to extract. Observation~\ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

>>>>

Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\alph*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 blog posts~\cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in the web feed.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building \emph{extraction rules} from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, to build an extraction rule capable of locating the target content on each HTML page.

% input from observations.
Observation~\ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as the blog post article (either abstract or full text), its title, authors and publication date. We call these fields \emph{targets} as they constitute the data our crawler aims to extract. Observation~\ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

### 2014-01-20 tex/3-architecture.tex
Seems pretty final to me
Add sucessfully printed Acrobat Distiller export
Minor
Done.

\begin{figure}
  \capstart
  \centering
  \includegraphics[width=0.47\textwidth]{scrapy_architecture}
  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, Scrapy$^1$)} % Could not found a way...
  \label{scrapyarchitecture}
\end{figure}

@@

In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation. The most frequent cases were blogs using the Disqus\footnote{\url{http://disqus.com/websites}} and LiveFyre \footnote{\url{http://web.livefyre.com}} comment hosting services. For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content. The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism~\cite{antinharasymiv2011}.

>>>>

\begin{figure}
  \capstart
  \centering
  \includegraphics[width=0.47\textwidth]{./img/scrapy_architecture.eps}
  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, Scrapy)}
  \label{scrapyarchitecture}
\end{figure}

@@

In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation. The most frequent cases were blogs using the Disqus\footnote{\url{http://disqus.com/websites}} and LiveFyre \footnote{\url{http://web.livefyre.com}} comment hosting services. For webmasters, these tools are very handy because the entire commenting infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content. The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism~\cite{antinharasymiv2011}.

### 2014-01-20 tex/4-evaluation.tex
Seems pretty final to me
Done.

As illustrated in \autoref{runningtime}, our approach spends the majority of it's total running time between the initialisation the processing of the first blog post. This initial increase of about 0.4 seconds corresponds to cost of executing \autoref{linearAlgo} to compute extraction rule for articles. As already mentioned, this consists in computing the \emph{best extraction rule} of each pages references by the web feed and picking the one functioning best on these pages. Once we have this extraction rule, processing subsequent blog posts only requires parsing and applying the rule, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}. The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.

The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post. Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach include the cost of entirely processing these 15 entries. That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variations of running times observed across programming languages~\cite{hundt2011}.

>>>>

As illustrated in \autoref{runningtime}, our approach spends the majority of its total running time between the initialisation and the processing of the first blog post. This initial increase of about 0.4 seconds corresponds to cost of executing \autoref{linearAlgo} to compute extraction rule for articles. As already mentioned, this consists of computing the \emph{best extraction rule} of each page referenced by the web feed and picking the most appropriate one. Once we have this extraction rule, processing subsequent blog posts only requires parsing and applying the rule, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}. The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.

The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post. Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach includes the cost of entirely processing these 15 entries. That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variation of running times observed across programming languages~\cite{hundt2011}.
